---
title: "Pre-calculated data for Universal Concept Signature calculation"
author:
- name: Xu Chi
  affiliation: Beijing Institute of Genomics, CAS, Beijing, China
output:
  BiocStyle::html_document:
vignette: >
  %\VignetteIndexEntry{Pre-calculated data for Universal Concept Signature calculation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Usage
```{r eval=FALSE}
data(preCal.data)
```

# Data format
***
The class of this dataset is list of characters. Each element of the list is a line of characters containing
the Entrez gene ID of a specific gene, the penalization factor of this gene in uniConSig algorithm, and the
coefficients of the related molecular concepts used in uniConSig calculation. The information is tab delimited.
After splitting, the first element is the Entrez gene ID, the second is the penalization factor, the
rest of the line are the molecular concepts and their coefficients.

```{r eval=FALSE}
#check the first element
data(preCal.data)
preCal.data[[1]]
```

# Installation
***

To install this package, start R and enter:
```{r eval=FALSE}
## try http:// if https:// URLs are not supported
source("https://bioconductor.org/biocLite.R")
biocLite("preCal.data")
```

# Sessioninfo
```{r}
sessionInfo()
```

